### 2023-04-18 chapter2/chapter2.tex
Added GO term analysis methods

\subsection{GO term analyses}

>>>>

\subsection{GO term analyses}
The 2022-03-22 go-basic release of the Gene Ontology was obtained from the GO Consortium website. The gene association file for the 2022\_02 release of the \textit{D. melanogaster} genome annotation was obtained from FlyBase. Obsolete annotations were dropped, and the remaining annotations were filtered by qualifiers and evidence code. The allowed qualifiers were ``enables,'' ``contributes\_to,'' ``involved\_in,'' ``located\_in,'' ``part\_of,'' and ``is\_active\_in.'' The allowed evidence codes were all experimental sources, traceable author statement (TAS), and inferred by curator (IC). The annotations were propagated up the ontology graph and joined with the region sets, so every annotation associated with a gene was associated with the regions derived from that gene. $P$-values were calculated with exact hypergeometric probabilities with regions considered as the sampling unit. For the disorder score analysis, the reference set was the filtered regions, and the enrichment set was regions in the upper decile of the score rate distribution. For the cluster analysis, the reference set was the filtered regions after the additional filtering by substitution rates, and the enrichments sets were the regions in each cluster.
